Wrattler: \textnormal{A platform for AI-assisted data science}

### 2018-03-15 report/paper.tex
fixing some typos

\item[--] AI assistants can access the dependency graph created for a
notebook. This allows the them to access the transformation history, which is the code
that has already been run during the analysis. The gives assistants information about the
context such as transformations that have already been performed.
\end{itemize}

@@

This makes it possible to exchange data efficiently. For example, a data frame where each cell
is annotated with a probabilistically inferred type will be significantly larger than a data
frame contianing just raw numbers. The content negotiation protocol allows the client to 
request a data frame with just raw numbers, significantly reducing the size.

>>>>

\item[--] AI assistants can access the dependency graph created for a
notebook. This allows them to access the transformation history, which is the code
that has already been run during the analysis. This gives assistants information about the
context such as transformations that have already been performed.
\end{itemize}

@@

This makes it possible to exchange data efficiently. For example, a data frame where each cell
is annotated with a probabilistically inferred type will be significantly larger than a data
frame containing just raw numbers. The content negotiation protocol allows the client to 
request a data frame with just raw numbers, significantly reducing the size.
